A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-02-14 manuscript/main.tex
Fri 14 Feb 2025 15:47:44 EST manuscript, timings, etc.

\section{Conclusion}
Depth is not always better!
Molecular representations specifically for QML
Distributed QC to incorporate more features

>>>>

\section{Conclusion}
Depth is not always better!
Molecular representations specifically for QML
Distributed QC to incorporate more features
Noiseless simulation is costly and does not offer the desired accuracy for BSE49 or DDCC

DDCC could be a useful dataset to benchmark PQC models since it is trivial to perform classically, yet hard for PQCs...
